Behavior Driven Development in Haskell

### 2012-06-02 paper.tex
make Haddock markup valid.

\begin{quote}
    sol: @kazu should we make the Haddock examples in this section
    valid Haddock comments?
\end{quote}

@@

\begin{quote}
\small
\begin{verbatim}
>>> writeFile "tmpfile" "Hello"
>>> readFile "tmpfile"
"Hello"
\end{verbatim}
\end{quote}

@@

\begin{quote}
\small
\begin{verbatim}
>>> head []
*** Exception: Prelude.head: empty list
\end{verbatim}
\end{quote}

@@

\begin{quote}
\small
\begin{verbatim}
prop> Data.Map.null empty == True
\end{verbatim}
\end{quote}

@@

\begin{quote}
\small
\begin{alltt}
prop> \verb|\|x -> null (takeExtension x) == \(\hookleftarrow\)
            not (hasExtension x)
\end{alltt}
\end{quote}

@@

\begin{quote}
\small
\begin{verbatim}
prop> \xs -> sort xs == (sort . sort) (xs :: [Int])
\end{verbatim}
\end{quote}

@@

\begin{quote}
\small
\begin{verbatim}
prop> sort xs == (sort . sort) (xs :: [Int])
\end{verbatim}
\end{quote}

>>>>

@@

\begin{quote}
\small
\begin{verbatim}
-- |
-- >>> writeFile "tmpfile" "Hello"
-- >>> readFile "tmpfile"
-- "Hello"
\end{verbatim}
\end{quote}

@@

\begin{quote}
\small
\begin{verbatim}
-- |
-- >>> head []
-- *** Exception: Prelude.head: empty list
\end{verbatim}
\end{quote}

@@

\begin{quote}
\small
\begin{verbatim}
-- |
-- prop> Data.Map.null empty == True
\end{verbatim}
\end{quote}

@@

\begin{quote}
\small
\begin{alltt}
-- |
-- prop> \verb|\|x -> null (takeExtension x) == \(\hookleftarrow\)
            not (hasExtension x)
\end{alltt}
\end{quote}

@@

\begin{quote}
\small
\begin{verbatim}
-- |
-- prop> \xs -> sort xs == (sort . sort) (xs :: [Int])
\end{verbatim}
\end{quote}

@@

\begin{quote}
\small
\begin{verbatim}
-- |
-- prop> sort xs == (sort . sort) (xs :: [Int])
\end{verbatim}
\end{quote}
